Simulating High-Dimensional Multivariate Data

### 2020-12-22 070-supplementary-materials.Rmd
4th draft. Fix funding information.

Research reported in this publication was supported by grants from NV INBRE and the National Institutes of General Medical Sciences (NIH 5U54GM104944, GM103440).

>>>>

Research reported in this publication was supported by grants from the National Institutes of General Medical Sciences (5 U54 GM104944, GM103440) from the National Institutes of Health.
